### 2020-11-16 05_Thesis/THESIS_LaTeX/Chapters/1.tex
chapter 1 done?

\begin{figure}[th]
\centering
\includegraphics[scale=0.40]{./Figures/CBNfingerprint.png}
\decoRule
\caption[Fingerprint of Carbon-based Nano-materials]{Molecular to mesoscale structural features of synthetic polymers influence the emergence of specific microstructural features in polymer-derived carbon materials after pyrolysis.}
\label{fig:CBNfingerprint}
\end{figure}

@@

\subsection{Carbon nanowires}

As depicted in Figure \ref{fig:carbonAllotropesDiagram}, carbon nano-fibers (CNFs) have been classified as linear, sp2-based structures. \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015, Vajtai2013} Nano-fibers own good electrical, optical and mechanical characteristics, however those properties are highly dependent on the morphology of the fibers. \cite{Dresselhaus2007} The material properties of 1D nano-structures depend on fiber diameter, porosity, crystallization degree and crystallization orientation. Consequently, the fabrication parameters and environment conditions have an impact on the reproducibility of high quality fibers. \cite{Dresselhaus2007}

Carbon nano-fibers (CNF) have diameters of several micrometers and are different from carbon nano-tubes (CNT). \cite{Weil1992, Huang2009, chung2012carbon, Subramoney1997, Dresselhaus2000}

\subsection{Nanowires synthesis}

%%%
Numerous methods to prepare nanowires, which include template-assisted synthesis [30], vapor–liquid-solid (VLS) [31], electrodeposition [32], electrospinning [33], hydrothermal [34], also hierarchical arrangement techniques [35–37] to organize the nanowires have been studies in the last ten years. Nanowires based on organic, inorganic or hybrid materials have been applied in order to get single or composites nanomaterials for innumerous purposes, such as chemical and biochemical sensing devices, thermoelectric, optical, magnetic and electrical application. In this section, we are focusing on the synthesis of conducting polymer and composites to develop materials in nanowires architectures.

\subsubsection{Synthesis of conducting polymer nanowires}

\subsection{\emph{conclude that NFES is the way to go}}

@@

@@

\subsection{General objective}
Study the practice and feasibility of a new fabrication process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner; by the integration of mechano-electrospinning technique.

>>>>

\begin{figure}[th]
\centering
\includegraphics[scale=0.37]{./Figures/CBNfingerprint.png}
\decoRule
\caption[Fingerprint of Carbon-based Nano-materials]{Molecular to meso-scale structural features of synthetic polymers influence the emergence of specific micro-structural features in polymer-derived carbon materials after pyrolysis.}
\label{fig:CBNfingerprint}
\end{figure}

@@

\subsection{Carbon Nano-wires}

As depicted in Figure \ref{fig:carbonAllotropesDiagram}, carbon nano-fibers (CNFs) have been classified as linear, sp2-based structures. \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015, Vajtai2013} Nano-fibers own good electrical, optical and mechanical characteristics, however those properties are highly dependent on the morphology of the fibers. \cite{Dresselhaus2007} The material properties of 1D nano-structures depend on fiber diameter, porosity, crystallization degree and crystallization orientation. Consequently, the fabrication parameters and environment conditions have an impact on the reproducibility of high quality fibers. \cite{Dresselhaus2007} Carbon nano-fibers (CNFs) have diameters of several micrometers (Figure \ref{fig:diameterComparisonOfCarbonFibers}) and are different from carbon nano-tubes (CNT). \cite{Weil1992, Huang2009, chung2012carbon, Subramoney1997, Dresselhaus2000} Unlike carbon nano-tubes with hollow cores, carbon nano-fibers can be represented as stacked layers along the thread length. \cite{Dresselhaus2000, Rodriguez1993, Yoon2004} The stacked geometry of carbon nano-fibers results in unique electrical, chemical and mechanical properties. \cite{Liu2009, Endo2003, Yokozeki2009} Unlike CNFs, carbon nano-tubes inherent problems such as high cost and low effective surface area, which limit their practical use. \cite{Vajtai2013}

\begin{figure}[th]
\centering
\includegraphics[scale=0.65]{./Figures/carbonFiberDiameterComparison.png}
\decoRule
\caption[Diameter comparison of various types of fibrous carbon materials]{Various types of fibrous carbon materials bear different characteristics according to their molecular structure. Adapted from \cite{Vajtai2013}}
\label{fig:diameterComparisonOfCarbonFibers}
\end{figure}

sp2 carbon nano-wires have been used for the improvement of power density and specific energy in lithium-ion batteries. \cite{Frackowiak2002, Endo2000, Winter1998} Authors posit that the performance and capacity of Li-ion batteries depend on the CNF structure and texture. Through the right combination of electrospinning and carbonization parameters, electrically conductive, mechanically tough and with thin diameter fibers have been achieved by Yoon et al. \cite{Yoon2004}. Yoon reported 431 mili-ampere-hour per gram batteries with vitreous carbon nanofibers. Yoon states that the battery capacity highly depends on the pyrolysis process parameters as the morphology of the fiber develops pores and hence different surface properties. CNFs supercapacitors have been investigated as energy storage devices due to their high power bearability and long lifecycles. \cite{Endo2001, Frackowiak2001, Pandolfo2006, Conway1999} The studies' authors posit that carbon nano-fibers can be implemented as high-power supercapacitors due to their large surface area and high electrical conductivity.

On the other hand, the low reactivity and unique morphology of CNFs make them promising catalyst supports for metal nano-particles. \cite{Choi2002, Li2002, Planeix1994} It is well known that the morphology and nano-structure of the supporting material are the main factors that prevent agglomerations of nano-particles. \cite{RomanMartinez1995, Serp2008} Moreover, in bone tissue scaffold applications, collagen is the most popular scaffold. However, collagen scaffolds bring xenogenicity issues which leads to disease transfer or immunogenic reactions, besides its inhability to preserve its shape once placed in the body. \cite{Bach1998, Butler1998, Delustro1990, Chachques2008, Atala2006, Glowacki2008, Valarmathi2008, Faraj2007} Currently, carbon fibers have been studied for bone tissue scaffold, however early attempts yield too thick fibers for cell cultivation and tissue regeneration. \cite{Visuri1991, Parsons1989} As depicted in previous research of CNFs for different applications, fiber morphology seems to have a significant impact on their performance.

Typically, carbon nano-fibers (CNFs) are synthesized by a combination of a patterning process and a pyrolysis process. CNFs fabricated by electrospinning of polymer solutions with electrostatic forces. Electrospun CNFs have characteristics such as high surface area, thin morphology with nano-scale diameters. The properties of electrospun fibers allow CNFs to be implemented in nano-sensing devices, energy storage applications, and tissue scafflods. \cite{Khanna2016, Ramakrishna2005, Reneker2000, Norris2000, Vozzi2002, Kim2003, Dersch2005} Several patterning techniques have been attempted to achieve the desired fiber morphology. In addition to electrospinning, CNFs have been also fabricated by two-photon polymerization (TPP) and photo-lithography techniques. \cite{CardenasBenitez2019} Cardenas et al. implemented TPP and conventional UV lithography to study the fabrication of CNFs within carbon micro-electromechanical systems.

@@

The role of carbon nano-fibers in nano-sensor devices play an important role, as portable instruments require light-weight and small-sized components. \cite{Khanna2016} Table \ref{tab:advantagesOfNanosensors} lists some advantages of nano-sensors that can be accomplished by the fabrication of CNFs via near-field electrospinning and a thermal treatment in an inert environment.

\begin{table}[ht]
\centering
\caption[Advantages of Nano-sensors]{Advantages of Nano-sensors. Adapted from \cite{Khanna2016}}
\begin{tabularx}{\textwidth}{lX}
\hline
\textbf{Advantage} & \textbf{Description} \\
\hline
High sensitivity & More accuracy, single molecule detection \\
Small size & Light-weight, portability, low-power consumption, small sample size, reduced sample preparation, and ease of use \\
Low response time & High-frequency, real time analysis \\
Low cost & Disposable devices \\
\hline
\end{tabularx}
\label{tab:advantagesOfNanosensors}
\end{table}

Sensors of small size require less time to output a stable signal as signals require less time to travel shorter lengths, hence signal noise is also reduced. Nano-sized sensors allow data collection and measurements to be performed in real time at faster speeds. \cite{Khanna2016} The nano-scale also allows sensors to increase the active surface area, enabling the absorption and detection of analytes in low concentrations. \cite{Khanna2016} The integration of small-sized sensing devices lean to lower fabrication costs as large-scale production and reproducible fabrication can be achieved when producing nanosensors. \cite{Khanna2016} Moreover, conventional sensors are bulky and require higher amounts of power to operate. In gas sensing, neither a large sensing surface or a large sample is required to get a readable output signal from the sensor. Power consumption can be saved by reducing the thermal mass of the sensor. \cite{Khanna2016} Furthermore, if several gases are to be detected, an array of several gas sensors are to be assembled into an array. A multi-gas sensor array can increase the size and cost, whereas an array of gas nano-sensors (each functionalized to detect a specific analyte) can be implemented into a single device. \cite{Khanna2016} Nano-sensors can be classified by the kind of energy or physycal phenomena that is detected, as depicted in Table \ref{tab:classificationOfNanosensors} for instance: biological, mechanical, thermal, chemical, and optical sensors. \cite{Khanna2016, BaudritJ2017}

\begin{figure}[th]
\centering
\includegraphics[scale=0.50]{./Figures/typesOfNanoSensors.png}
\decoRule
\caption[Types of Nano-sensors]{Diagram examples of carbon-based nano-sensors. Adapted from \cite{BaudritJ2017}}
\label{fig:diameterComparisonOfCarbonFibers}
\end{figure}

\begin{table}[ht]
\centering
\caption[Classification of Nano-sensors]{Classification of Nano-sensors. Adapted from \cite{Khanna2016}}
\begin{tabularx}{\textwidth}{lX}
\hline
\textbf{Classification} & \textbf{Phenomena / Energy} \\
\hline
Mechanical & Position, acceleration, stress, strain, force, pressure, mass, density, viscosity, moment, torque \\
Acoustic & Wave amplitude, phase, polarization, velocity \\
Optical & Absorbance, reflectance, fluorescence, luminescence, refractive index, light scattering \\
Thermal & Temperature, flux, thermal conductivity, specific heat \\
Electrical & Charge, current, potential, dielectric constant, conductivity \\
Magnetic & Magnetic field, flux, permeability \\
Chemical & Components (identities, concentrations, states) \\
Biological & Biomass (identities, concentrations, states) \\
\hline
\end{tabularx}
\label{tab:classificationOfNanosensors}
\end{table}

@@

\subsection{General objective}
Study the practice and feasibility of a new fabrication process to achieve mass scale manufacturing of polymeric micro-wires in an inexpensive, continuous, simple and reproducible manner by the integration of near-field electromechanical spinning (NFEMS) and forward-thinking on pyrolysis processes to convert polymeric micro-wires into carbon nano-wires.
